Stat_490_Paper

### 2020-05-08 Paper.Rmd
Model Summaries Added
Current Progress

![Scan 1 Sampled](/Users/piza7/Pictures/Paper_1_samp.png)

@@

![Scan 1](/Users/piza7/Pictures/Paper_1_nosamp.png)

@@

- In the beginning of this paper we talked about bullets being numerically characterized, which we said were features.  One of these features is CMS, also known as consecutive matching striae.  We are now able extract the CMS and all the other features associated with bullets land impression.  We first smooth the signatures(See Figure 8), identifiy peaks and valleys of each signature(See Figure 9), and align every signature with eachother(See Figure 10). When the two signatures are aligned we are able to identify the matching peaks and valleys which coincide to the striation marks left on a bullet's surface after being fired(See figure 11). This is done by using the sig_aligned() function in the bulletxtrctr package. Notice the word "striation," that's right these are our consecutive matching striae. We can calculate the consecutive matching striae using the sig_cms_max() function in the bulletxtrctr package.

@@

[1] implies same comparisons are kept for statistical summary

[2] implies same comparisons are removed for statistical summary

0.000   2.000   3.000   3.141   4.000  73.000 [1]

0.000   2.000   3.000   2.872   4.000  34.000 [2]

@@

@@

>>>>

@@

@@

- In the beginning of this paper we talked about bullets being numerically characterized, which we said were features.  One of these features is CMS, also known as consecutive matching striae.  We are now able to extract the CMS and all the other features associated with bullets land impression.  We first smooth the signatures(See Figure 8), identifiy peaks and valleys of each signature(See Figure 9), and align every signature with eachother(See Figure 10). When the two signatures are aligned we are able to identify the matching peaks and valleys which coincide to the striation marks left on a bullet's surface after being fired(See figure 11). This is done by using the sig_aligned() function in the bulletxtrctr package. Notice the word "striation," that's right these are our consecutive matching striae. We can calculate the consecutive matching striae using the sig_cms_max() function in the bulletxtrctr package.

@@

[1*] implies same comparisons are kept for statistical summary

[2*] implies same comparisons are removed for statistical summary

```{r}

library(readxl)
Same_Comparisons_Kept <- read.csv("Book1.csv", header = T)

Same_Comparisons_Removed <- read.csv("book2.csv", header = T)

### Same_Comparisons_Kept

```{r}

head(Same_Comparisons_Kept, 8)

### Same_Comparisons Removed

```{r}

head(Same_Comparisons_Removed, 8)

- Looking at the CMS statistics for Same_Comparisons_Removed the lower values of span have higher mean and max statistics. The distribution seems to be skewed to the right. Now that we have corrected the resolution the CMS statistics are not the same as last time.  We tended to see the highest average results for spans of 55 to 75.  These results suggest we perform less smoothing.

@@

- Notice, for all span values we see slight separability.  The CMS feature does seem to explain some of the models ability to distinquish between Matchs and Non-matches.

## Model Summary RF

*90 10 split*

  Reference

Prediction FALSE TRUE

     FALSE  3729  103

     TRUE     16   72

*80 20 split*

   Reference

Prediction FALSE TRUE

     FALSE  7357  187

     TRUE    133  163

*70 30 split*

   Reference

Prediction FALSE  TRUE

    FALSE 11178   311

    TRUE     57   214

@@

0.000   2.000   3.000   3.141   4.000  73.000 [1*]

0.000   2.000   3.000   2.872   4.000  34.000 [2*]
